\section*{Biography}

Thomas Gaussiran is the director of the Space and Geophysics
Laboratory (SGL) at  \mbox{Applied Research Laboratories},
The University of Texas at Austin (ARL:UT). He received his B.S. in
Physics from UT Austin (1988) and M.S. (1991) and Ph.D. (1994) from
Rice University.

Eric Hagen is a graduate student in the Department of
Aerospace Engineering and Engineering Mechanics at UT Austin.

R. Benjamin Harris is an Engineering Scientist at ARL:UT.  He received a B.S. (1994) and Ph.D. (2008) in Aerospace Engineering from UT Austin and his M.S. in Aeronautics and Astronautics from \mbox{Stanford (2000)}.

Chris Kieschnick is an Engineering Scientist Associate at ARL:UT. Chris received his B.S. (2009) in Computer Science from UT Austin.

Jon Little is a Senior Engineering Scientist at ARL:UT. He obtained a
B.S. (1988) and a M.S. (1990) from Auburn.

Richard Mach is a project lead at ARL:UT.  He has been involved with
GPS applications since 1990.  He holds a B.S. (1990) and M.S. (1992)
in Aerospace Engineering from UT Austin.

David Munton is a Research Associate at ARL:UT. He earned a B.S. in Physics from Sonoma State University (1982), and a Ph.D. in Physics from UT Austin (1992). 

Scot Nelsen is an Engineering Scientist at ARL:UT. He earned a B.S. in
Electrical Engineering at UT Austin (1998).

Colin Petersen is an Engineering Scientist Associate at ARL:UT. He received a B.S. (2004) and M.S. (2006) in Electrical and Computer Engineering from UT Austin.

David Rainwater is a Research Associate at ARL:UT. He received a B.S. in Physics from the University of Missouri (1993) and a Ph.D. in Physics from the University of Wisconsin Madison (1999).

Brent Renfro is a program manager at ARL:UT.  He has a B.A. in Physics from Wabash College (1979) and a M.A. in Computer Science from UT Austin (1983).

Brian Tolman is a Research Scientist at ARL:UT. He holds a
Ph.D. in theoretical physics from UT Austin (1982).

Dagoberto Salazar is an Aeronautical Engineer (IUPFAN, Venezuela, 1992). After working several years both for government and private industry, he pursued postgraduate studies in Instrumentation and Control (UCV). He is currently a Ph.D. candidate in Aerospace Science and Technology at the Universitat Polit\`{e}cnica de Catalunya (UPC, Spain).

