\section*{Future}

The most significant change planned in the near term for the GPSTk is
that the RINEX-3 branch that will be integrated into the main. This
will result in a major revision change for the source code, resulting
in the release of GPSTk 2.0. As with other projects, when a major
version number changes, that indicate the new code is not backwards
compatible. Given the magnitude of such a change, a pre-release
version of GPSTk 2.0 may be released to facilitate testing. The
details regarding this transition will be discussed on the developer's
mail list hosted by SourceForge,
\gpstkclass{gpstk-devel@lists.sourceforge.net}. Once finalized, the
plan for transition to GPSTk 2.0 will be announced using another SF
hosted mail list, \gpstkclass{gpstk-announce@lists.sourceforge.net}.

Smaller changes are also planned. The \gpstkapp{libsatvis} library
will be added. This library will require extracting detailed
visualizations from existing software, some of which are yet to be
contributed to the GPSTk. Another library modification involves
providing library calls to other programming languages such as
Python and Octave. The interface that supports these languages is
being redesigned and updated. Applications modifications are
underway as well. The \gpstkapp{mpsolve} application is being
extended to solve and remove the biases associated with carrier phase.  This
technique will provide an essentially bias-free estimate of
range-minus-phase multipath. These detailed extensions to the GPSTk
will be the subject of future papers. 

The aforementioned future modifications are only those planned by
contributors at ARL:UT. The GPSTk is a community project, therefore,
like all GNSSs, its future is open-ended.
