%\documentclass{article}
%\usepackage{fancyvrb}
%\usepackage{perltex}
%\usepackage{xcolor}
%\usepackage{listings}
%\usepackage{longtable}
%\usepackage{multirow}
%\input{src/cmd}
%\begin{document}

\index{ash2mdp!application writeup}
\index{ash2xyz!application writeup}
\section{\emph{ash2mdp ash2xyz}}
\subsection{Overview}
These applications process Ashtech Z(Y)-12 observation and ephemeris data and output satellite positions and ionospheric corrections in either MDP or XYZ format.
\subsection{Usage}

\subsubsection{\emph{ash2mdp ash2xyz}}

\begin{\outputsize}
\begin{longtable}{lll}
%\multicolumn{3}{c}{\application{ash2mdp} \application{ash2xyz}} \\
\multicolumn{3}{l}{\textbf{Optional Arguments}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{-i}{}{Where to get data from.  The default is to use stdin.}{2}
\entry{-o}{}{Where to send the output.  The default is to use stdout.}{2}
\entry{-d}{--debug}{Increase debug level.}{1}
\entry{-v}{--verbose}{Increase verbosity.}{1}
\entry{-h}{--help}{Print help usage.}{1}
\entry{-w}{--week=NUM}{The full GPS week in which this data starts.  Use this option when the start time of the data being processed is not during this week.}{3}
\entry{-c}{--code=ARG}{Restriction for source of observation data collected via L1/L2 Y code tracking will be used.  Options are "Y", "P", and "codeless." XYZ only.}{4}
\entry{-s}{--offset=NUM}{Output SV positions at a time offset from the current time.  Give a positive or negative integer of seconds. XYZ only.}{3}
\entry{-n}{--num\_points=NUM}{Width of the exponential filter moving window, in number of points (default is 36).  XYZ only.}{3}
\end{longtable}
\end{\outputsize}

\subsection{Notes}
Input is on the command line, or of the same format in a file (-f$<$file$>$).

%\end{document}
