%\documentclass{article}
%\usepackage{fancyvrb}
%\usepackage{perltex}
%\usepackage{xcolor}
%\usepackage{listings}
%\usepackage{longtable}
%\usepackage{multirow}
%\input{src/cmd}
%\begin{document}

\index{daa!application writeup}
\section{\emph{daa}}
\subsection{Overview}
This application performs a data availability analysis of the input data. In general, availability is determined by station and satellite position.

\subsection{Usage}
\subsubsection{\emph{daa}}
\begin{\outputsize}
\begin{longtable}{lll}
%\multicolumn{3}{c}{\application{daa}} \\
\multicolumn{3}{l}{\textbf{Required Arguments}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{-e}{--eph=ARG}{Where to get the ephemeris data.  Acceptable formats include RINEX nav, FIC, MDP, SP3, YUMA, and SEM.  Repeat for multiple files.}{3}
\entry{-o}{--obs=ARG}{Where to get the observation data.  Acceptable formats include RINEX obs, MDP, smooth, Novatel, and raw Ashtech.  Repeat for multiple files.  If a RINEX obs file is provided, the position will be taken from the header unless otherwise specified.}{5}
& & \\
\multicolumn{3}{l}{\textbf{Optional Arguments}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{-d}{--debug}{Increase debug level.}{1}
\entry{-v}{--verbose}{Increase verbosity.}{1}
\entry{-h}{--help}{Print help usage.}{1}
\entry{}{--ouput=ARG}{Output location (default is stdout).}{1}
\entry{-x}{--independent=ARG}{The independent variable in the analysis.  The default is time.}{2}
\entry{-c}{--msc=ARG}{Station coordinates file.}{1}
\entry{-m}{--msid=ARG}{Station for which to process data.  Used to select a station position from the msc file.}{2}
\entry{-t}{--time-format=ARG}{CommonTime format specifier used for times in the output.  The default is \lq\lq\%Y \%j \%02H:\%02M:\%04.1f\rq\rq.}{3}
\entry{}{--mask-angle=ARG}{Ignore anomalies on SVs below this elevation.  
	The default is 10 degrees.}{2}
\entry{}{--track-angle=ARG}{Assume the receiver starts tracking at this elevation.
	The default is 10 degrees.}{2}
\entry{}{--time-mask=ARG}{Ignore anomalies on SVs that haven't been above the mask angle for this number of seconds.
	The default is 0 seconds.}{3}
\entry{}{--snr=ARG}{Discard data with an SNR less than this value. 
	The default is 20 dB-Hz.}{2}
\entry{-p}{--position=ARG}{Receiver antenna position in position (x,y,z) coordinates. 
	Format as a string: ``X Y Z".}{2}
\entry{-l}{--time-span=ARG}{How much data to process, in seconds.}{1}
\entry{}{--ignore-prn=ARG}{Specify the PRN of an SV to not report on in the output. Repeat to specify multiple SVs.}{2}
\entry{}{--obs-interval=ARG}{Specify the time interval, in seconds, between observations. The default is to scan the file to discover this via examination of the file.}{3}
\entry{-b}{--bad-health}{Ignore anomalies associated with SVs that are marked unhealthy.}{2}
\entry{-s}{--smash-adjacent}{Combine adjacent lines from the same PRN.}{1}
\entry{}{--start-time=TIME}{Ignore data before this time.}{1}
\entry{}{--stop-time=TIME}{Ignore any data after this time.}{1}
\end{longtable}
\end{\outputsize}

\subsection{Examples}
\begin{verbatim}
> daa -o s121001a.05o -e s121001a.05n

 Availability Raw Results :

Start                 End        #     PRN    Elv          Az  Hlth  ama ata
============================================================================
2005 1 00:06:30.0              1     4    10.03^         316   0     8   9   
2005 1 00:07:00.0              1     4    10.20^         316   0     8   9   
2005 1 00:07:30.0              1     4    10.38^         316   0     8   9   
2005 1 00:08:00.0              1     4    10.55^         315   0     8   9   
2005 1 00:08:30.0              1     4    10.73^         315   0     8   9   
2005 1 00:09:00.0              1     4    10.91^         315   0     8   9   
2005 1 00:12:30.0              1     4    12.13^         314   0     8   9   
+L1 GPSP,L2 GPSP
2005 1 00:26:30.0              1     24   10.36^         313   0     8   9  
+L1 GPSP,L2 GPSP
2005 1 02:02:30.0              1     11   10.02v         123   0     7   9   
2005 1 03:09:00.0              1     20   10.11v         141   0     8   10  
...
2005 1 22:28:00.0              1     20   10.50^          24   0     7   9   
2005 1 22:30:00.0              1     20   11.04^          25   0     7   9   
2005 1 22:30:30.0              1     20   11.17^          25   0     7   9   
2005 1 22:31:00.0              1     20   11.31^          25   0     7   9   
2005 1 22:33:00.0              1     20   11.86^          26   0     7   9   
+L1 GPSP,L2 GPSP
2005 1 22:49:30.0              1     3    10.00v         117   0     7   9   
2005 1 22:52:00.0              1     7    10.04^         273   0     7   9   
+L1 GPSP,L2 GPSP

 Summary:

Analysis span: 2453372 00000000 0.000000000000000 GPS through 2453372 86370000 
0.000000000000000 GPS
Data span:     2453372 00000000 0.000000000000000 GPS through 2453372 86370000 
 0.000000000000000 GPS
Total number of epochs with data: 2880
Epochs with any data missing: 184
Epochs without data from any SV: 0
SV-Epochs expected: 23234
Channel Loss: 0.00000 % (0)
SV-Epochs missed: 0.71017 % (165)
\end{verbatim}

%\end{document}
