%\documentclass{article}
%\usepackage{fancyvrb}
%\usepackage{perltex}
%\usepackage{xcolor}
%\usepackage{listings}
%\usepackage{longtable}
%\usepackage{multirow}
%\input{src/cmd}
%\begin{document}

\index{DiscFix!application writeup}

\section{\emph{DiscFix}}
\subsection{Overview}
This application reads a RINEX observation data file containing GPS dual-frequency pseudorange and carrier phase measurements, divides the data into `satellite passes', and finds and fixes discontinuities in the phases for each pass.

Output is a list of editing commands for use with program EditRinex. DiscFix will (optionally) write the corrected pseudorange and phase data to a new RINEX observation file. Other options will also smooth the pseudorange and/or debias the corrected phase. 

DiscFix calls the GPSTk Discontinuity Corrector (GDC vers 5.3 7/14/2008).

\subsection{Usage}
\subsubsection{\emph{DiscFix}}
\begin{\outputsize}
\begin{longtable}{lll}
%\multicolumn{3}{c}{\application{DiscFix}} \\
\multicolumn{3}{l}{\textbf{Required Arguments}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{}{--inputdir}{File containing more options.}{1}
\entry{}{--dt}{Time space in seconds of the data.}{1}
& & \\
\multicolumn{3}{l}{\textbf{Optional Arguments}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{-f}{--file}{File containing more options.}{1}
\entry{}{--beginTime}{Start time of processing (BOF).}{1}
\entry{}{--endTime}{End time of processing (EOF).}{1}
\entry{}{--decimate}{Decimate data to specified time interval, in seconds.}{2}
\entry{}{--forceCA}{Use C/A code range, NOT P code. Default only if P absent.}{2}
\entry{}{--gap}{Minimum data gap in seconds separating satellite passes (600).}{2}
\entry{}{--onlySat}{Process only satellite (GPS SatID, e.g. G21).}{1}
\entry{}{--exSat}{Exclude satellite(s) (GPSSatID).}{1}
\entry{}{--smoothPR}{Smooth pseudorange and output in place of raw pseudorange.}{2}
\entry{}{--smoothPH}{Debias phase and output in place of raw phase.}{1}
\entry{}{--smooth}{Same as --smoothPR AND --smoothPH.}{1}
\entry{}{--{DClabel}}{Set Discontinuity Corrector parameter `label' to `value'.}{2}
\entry{}{--DChelp}{Print a list of GDC parameters and their defaults, then quit.}{2}
\entry{}{--logOut}{Output log file name (df.log).}{1}
\entry{}{--cmdOut}{Output file name, for editing commands (df.out).}{2}
\entry{}{--format}{Output time format (gpstk::CommonTime) (\%4F \%10.3g).}{2}
\entry{}{--RinexFile}{RINEX (obs) file name for output of corrected data.}{2}
\entry{}{--RunBy}{RINEX header `RUN BY' string for output.}{1}
\entry{}{--Observer}{RINEX header `OBSERVER' string for output.}{1}
\entry{}{--Agency}{RINEX header `AGENCY' string for output.}{1}
\entry{}{--Marker}{RINEX header `MARKER' string for output.}{1}
\entry{}{--Number}{RINEX header `NUMBER' string for output.}{1}
\entry{-h}{--help}{Print this syntax page and quit.}{1}
\entry{}{--verbose}{Print extended output to the log file.}{1}

\end{longtable}
\end{\outputsize}

\subsection{Examples}
\begin{\outputsize}
\begin{verbatim}
> DiscFix --dt 1.5 --inputfile ar12800.06o

DiscFix, part of the GPS ToolKit, Ver 5.0 8/20/07, Run 2011/07/22 11:17:25
DiscFix is writing to log file df.log
DiscFix is writing to output file df.out
DiscFix timing: 0.960 seconds.

\end{verbatim}
\end{\outputsize}
%\end{document}
