%\documentclass{article}
%\usepackage{fancyvrb}
%\usepackage{perltex}
%\usepackage{xcolor}
%\usepackage{listings}
%\usepackage{longtable}
%\usepackage{multirow}
%\input{src/cmd}
%\begin{document}

\index{IonoBias!application writeup}

\section{\emph{IonoBias}}
\subsection{Overview}
The application will open and read several preprocessed RINEX observation files (containing obs types EL, LA, LO, SR or SS) and use the data to estimate satellite and receiver biases and to compute a simple ionospheric model using least squares and the slant TEC values.

\subsection{Usage}
\subsubsection{\emph{IonoBias}}
\begin{\outputsize}
\begin{longtable}{lll}
%\multicolumn{3}{c}{\application{IonoBias}} \\
\multicolumn{3}{l}{\textbf{Required Arguments}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{}{--input}{Input RINEX obs file name(s).}{1}
& & \\
\multicolumn{3}{l}{\textbf{Optional Arguments}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{-f}{}{File containing more options}{1}
\entry{}{--inputdir}{Path for input file(s).}{1}
& & \\
\multicolumn{3}{l}{\textbf{Ephemeris Input}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{}{--navdir}{Path of navigation file(s).}{1}
\entry{}{--nav}{Navigation (RINEX (nav) OR SP3) file(s).}{1}
& & \\
\multicolumn{3}{l}{\textbf{Output}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{}{--datafile}{Data (AT) file name, for output and/or input.}{1}
\entry{}{--log}{Output log file name.}{1}
\entry{}{--biasout}{Output satellite+receiver biases file name.}{1}
& & \\
\multicolumn{3}{l}{\textbf{Time Limits}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{}{--BeginTime}{Start time, arg is of the form YYYY,MM,DD,HH,Min,Sec.}{2}
\entry{}{--BeginGPSTime}{Start time, arg is of the form GPSweek,GPSsow.}{2}
\entry{}{--EndTime}{End time, arg is of the form YYYY,MM,DD,HH,Min,Sec.}{2}
\entry{}{--EndGPSTime}{End time, arg is of the form GPSweek,GPSsow.}{2}
& & \\
\multicolumn{3}{l}{\textbf{Processing}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1} 
\entry{}{--NoEstimation}{Do NOT perform the estimation (default=false).}{1}
\entry{}{--NoPreprocess}{Skip preprocessing; read (existing) AT file (false).}{2}
\entry{}{--NoSatBiases}{Compute Receiver biases ONLY (not Rx+Sat biases) (false).}{2}
\entry{}{--Model}{Ionospheric model: type is linear, quadratic or cubic.}{2}
\entry{}{--MinPoints}{Minimum points per satellite required.}{1}
\entry{}{--MinTimeSpan}{Minimum timespan per satellite required (minutes).}{2}
\entry{}{--MinElevation}{Minimum elevation angle (degrees).}{1}
\entry{}{--MinLatitude}{Minimum latitude (degrees).}{1}
\entry{}{--MaxLatitude}{Maximum latitude (degrees).}{1}
\entry{}{--MinLongitude}{Minimum longitude (degrees).}{1}
\entry{}{--MaxLongitude}{Maximum longitude (degrees).}{1}
\entry{}{--TimeSector}{Time sector (day | night | both).}{1}
\entry{}{--TerminOffset}{Terminator offset (minutes).}{1}
\entry{}{--IonoHeight}{Ionosphere height (km).}{1}
& & \\
\multicolumn{3}{l}{\textbf{Other Options}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{}{--XSat}{Exclude this satellite ($<$sat$>$ may be $<$system$>$ only).}{2}
\entry{-v}{--verbose}{Print extended output info.}{1}
\entry{-d}{--debug}{Increase debug level.}{1}
\entry{-h}{--help}{Print syntax and quit.}{1}

\end{longtable}
\end{\outputsize}

\subsection{Examples}
\begin{\outputsize}
\begin{lstlisting}
> IonoBias --inputdir data_set --navdir data_set --input s081213a.99o --input s081214a.99o
--input s081215a.99o --nav s081213a.99n --nav s081214a.99n --nav s081215a.99n --datafile output}
IonoBias, built on the GPSTK ToolKit, Ver 1.0 6/25/04, Run 2006/08/17 09:50:59
IonoBias output directed to log file IonoBias.log
IonoBias timing: 6.210 seconds.
\end{lstlisting}

\begin{verbatim}
Output File Snippet

    3     3 Number (max, good) stations in this file
010101101100001111110111011101110
010101101100001111110111011101110
010100101100001111110111011101110
Npt  9737 Sta 85408 LLH    30.2160   262.2746   163.4226
1021      0.0   0.00000 -463513.64930 0.32    0.000      1  1   1
1021      0.0   0.00000 -463513.64930 0.32    0.000      1 14   1
1021      0.0   0.00000 -463513.64930 0.32    0.000      1 15   1
1021      0.0   0.00000 -463513.64930 0.32    0.000      1 21   1
1021      0.0   0.00000 -463513.64930 0.32    0.000      1 22   1
1021      0.0   0.00000 -463513.64930 0.32    0.000      1 25   1
1021      0.0   0.00000 -463513.64930 0.32    0.000      1 29   1
1021      0.0   0.00000 -463513.64930 0.32    0.000      1 30   1
1021     30.0   0.00000 -463513.52430 0.32    0.000      1  1   1
1021     30.0   0.00000 -463513.52430 0.32    0.000      1 14   1

\end{verbatim}

\end{\outputsize}

\subsection{Notes}
Input can be either on the command line or put in a file and then input using the -f option. The file is formatted just as if
it were the command line.

%\end{document}

