%\documentclass{article}
%\usepackage{fancyvrb}
%\usepackage{src/perltex}
%\usepackage{src/xcolor}
%\usepackage{listings}
%\usepackage{longtable}
%\usepackage{multirow}
%\input{src/cmd}
%\begin{document}

\index{rtAshtech!application writeup}
\section{\emph{rtAshtech}}
\subsection{Overview}
This application logs observations from an Ashtech Z-XII receiver. It records
observations directly into the RINEX format. A number of optional outputs are
possible. The raw messages from a receiver can be recorded. Observations can
also be recorded in a format that is easily imported into numerical packages.

\subsection{Usage}
\begin{\outputsize}
\begin{longtable}{lll}
%\multicolumn{3}{c}{\application{rtAshtech}} \\
\multicolumn{3}{l}{\textbf{Optional Arguments}} \\
\entry{Short Arg.}{Long Arg.}{Description}{1}
\entry{-h}{--help}{Print help usage.}{1}
\entry{-v}{--verbose}{Increased diagnostic messages.}{1}
\entry{-r}{--raw}{Record raw observations.}{1}
\entry{-l}{--log}{Record log entries.}{1}
\entry{-t}{--text}{Record observations as simple text files.}{1}
\entry{-o}{--rinex-obs=ARG}{Naming convention for RINEX obs files.}{1}
\entry{-n}{--rinex-nav=ARG}{Naming convention for RINEX nav message files.}{2}
\entry{-T}{--text-obs=ARG}{ Naming convention for obs in simple text files.}{1}
\entry{-i}{--input}{Where to read ashTech data.  Can be a file or a serial device (ser:/dev/ttyS0), a tcp port (tcp:hostname:port), or standard input (the default).}{2}
\end{longtable}
\end{\outputsize}

\subsection{Examples}
\begin{\outputsize}
\begin{lstlisting}
> rtAshtech -p /dev/ttyS1
\end{lstlisting}
\end{\outputsize}

\begin{\outputsize}
\begin{lstlisting}
> rtAshtech -o "minute\%03j\%02H\%02M.\%02yo"
\end{lstlisting}
\end{\outputsize}

\subsection{Notes}
\application{rtAshtech} only works on UNIX systems with POSIX compliant serial ports.

%\end{document}
